\subsubsection{\textsubscript{\uppercase{\texttt{Oct 2018--Present}}\\
Founder / Leader / Software Engineer at Pseudomode}}
Founded Workshop for making not only \uppercase{accessible} but \uppercase{usable} Technologies.
\paragraph{Bostagy:}
A WebSocket server for Shell using NodeJS.
It exposes a NodeJS module and Shell command that run a WebSocket server at the specified address and port;
connecting the client via WebSocket protocol to standard streams of the Bostagy process.
It implements the WebSocket protocol on top of the http core module.
\paragraph{Maitre:}
A Web server for Shell using NodeJS.
It exposes a Shell command that runs a Web server on the specified address and port.
When a client connects via WebSocket protocol or sends an HTTP request,
Maitre searches for either a wsrc file or a file whose name is starts with the HTTP verb (get, post, put, etc.) and the rc suffix.
If the file is found successfully, Maitre runs the commands found in this file in a child process and connects the client to its standard streams.
\paragraph{Scenarist:}
A Scenario-based UI framework.
A Scenarist application consists of scenarios.
Each scenario is run by characters.
When the user selects a character in a scenario,
the character plays it's scene by saying it's dialog (can be some HTML if run in a browser or plain text if run on a TTY, and so on)
and does it's action (switch to a different scenario or whatever function the application designer assigns.).
\paragraph{Oscilla:}
A Sound Synthesizer for Shell.
It uses Scenarist to build the UI and Csound for it's logic.
In each scenario of Oscilla,
ASCII codes are considered as the scenario characters.
For instance, when on the Note scenario,
the 's' ASCII code triggers the character responsible for playing the C pitch,
and 'g' triggers the character responsible for decrementing the octave, and so forth.
\paragraph{Nota:}
A Database platform for Shell.
The user organise their data in notebooks.
Each notebook has a note pattern.
Notes belong to a note book will have the same structure as the note pattern.
Each note consists of a collection of fields.
Each field has a tag name and value.
