\subsubsection{\textsubscript{\uppercase{\texttt{Jan 2011--Nov 2011}}\\
Junior Software Engineer at TekTrust}}
\begin {enumerate}
\item Took a training on Business Process Management using Appian BPM Suite to:
\begin {itemize}
\item Design and model processes using Appian Process Modeler.
\item Design applications using Appian Applications designer.
\item Design forms using Appian forms designer.
\item Customize smart services, expression functions, custom forms and custom channels using Appian java APIs,
JSP, HTML, Javascript, CSS and other web technologies.
\end {itemize}
\item As a member of a team of 3, built now kora social network connecting soccer players using Elgg open
source social networking engine (MVC framework based on LAMP):
\begin {itemize}
\item Designed and implemented an Elgg plugin for linking the users now kora account with his facebook account
using the facebook graph API, it allows the user to login using facebook and updates his timeline with his now
kora feeds.
\item Designed and implemented a plugin for organizing soccer matches between players in the network. The plugin
allows a team's admin to create/edit/delete matches, invite team players to created matches and accept/reject
non-team players join requests.
\item Contributed in the Design and implementation of an Elgg web theme for all the pages the pages that appear
when there is no user logged in using HTML4, CSS2 and jQuery UI.
\item Designed and implemented two mobile Elgg views, one for touch devices using Sencha Touch 2 and the other
for blackberry devices using JQuery Mobile. During this task, I had to customize a lot of javascript, jQuery,
HTML5 and CSS3 code to build the UI as required by the client.
\end {itemize}

\end {enumerate}
